### 2019-03-27 _publications/jors/paper.tex
Extend the intro

\section*{Introduction (new)}

Generally, small scientific communities do not have the resources to
build and host dedicated web infrastructure to support their varied
content and data requirements. In particular, hosting and supporting a
complex content management system (CMS) including web servers, web
frameworks and databases requires a great deal of configuration and
long term support and funding. Furthermore, a turnkey CMS solution may
not meet requirements for a particular scientific group that may
require arcane data formats, custom data displays and client-side
automation. The PFHub effort, instead of focusing on the CMS tool,
focuses on customizing and delivering the "client-side" requirements
whilst delegating back-end functionality to external services that
provide dependable APIs~\cite{cmsfree}.

@@

This paper presents the first deployment of the PFHub framework
including its ``client-side'' focused design, how it employs external
services and meta-data about the code base.

>>>>

\section*{Introduction}

Generally, small scientific communities do not have the resources to
build and host dedicated web infrastructure to support their varied
content and data requirements. In particular, hosting and supporting a
complex content management system (CMS) including web servers, web
frameworks and databases requires a great deal of configuration and
long term support and funding. Furthermore, a turnkey CMS solution may
not meet requirements for a particular scientific group that may
require arcane data formats, custom data displays and client-side
automation. The PFHub effort, instead of focusing on the CMS tool,
focuses on customizing and delivering the client-side requirements
whilst delegating back-end functionality to external services that
provide dependable APIs~\cite{cmsfree}.

@@

This paper presents the first deployment of the PFHub framework
including its client-side focused design, how it employs external
services and meta-data about the code base. The paper describes the
relative ease with which other scientific groups might adapt the
framework for their own purposes and deploy using the fully
reproducible Nix environment~\cite{nix}.
